### 2021-10-25 paper/output/document/upshot.tex
a solution i guess

Once I realized this logical property, I tried to understand its philosophical plausibility. I 
wanted to philosophically test the hypothesis that maxims in which  $(c \longrightarrow a) \vee 
(c \longrightarrow g)$ are not valid inputs to the FUL. I concluded that because vacuous maxims neither 
change an agent's behavior nor generate meaningful obligations, they are not the right kinds of questions 
for practical reasoners to be asking. They cannot be action-guiding and are thus not the domain of ethics.

I define a vacuous maxim as one in which the circumstances entail either the act or the goal. An example
of a vacuous maxim is: ``When eating breakfast, eat breakfast in order to eat breakfast." This 
maxim isn't clearly obligatory or prohibited, but there is something empty about it. For one 
thing, acting on this maxim would never result in any actual action. If an agent adopts this maxim, 
they decide that, in the circumstances ``eating breakfast" they will perform the act ``eating breakfast"
for the purpose ``eating breakfast." In these circumstances, the act has 
already been performed! Making this maxim a rule to live by doesn't change how you live your life. If 
you adopt this maxim, when you are eating breakfast, you eat breakfast, but this statement is already 
tautologically true.

Not only does a vacuous maxim fail to prescribe action, any obligations or prohibitions it 
generates have already been fulfilled or violated and are thus foregone conclusions. If a vacuous 
maxim generates a prohibition, then this prohibition would be impossible to obey. 
It is impossible to not eat breakfast while eating breakfast, because the circumstances assume that the 
act has happened. On the other hand, if a vacuous maxim generates an obligation, then the obligation 
will have already been fulfilled. If you are required to eat breakfast while eating breakfast, then you've 
already fulfilled your obligation because the circumstances assume that the act has happened. Thus, 
a vacuous maxim does not actually guide action because it doesn't generate new obligations or 
prohibitions that could ever be acted on.

If any obligations or prohibitions generated by vacuous maxims do not tell us how to live, such 
maxims must not be the domain of ethics because ethics is 
supposed to tell us how to live. Kant's categorical imperative
 guides our use of practical reason, which is the kind of reason that tells us what we should do. 
A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
because the reasoner wants to know how to act. Practical reason is action-guiding, but a vacuous
 maxim can never be action-guiding because it prescribes no new
actions or obligations. It is not the kind of maxim that a practical reasoner would consider. 
There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
is the wrong kind of question for a practical reasoner to ask. Moreover, an ordinary person trying 
to navigate the world would never ask that kind of question. If ethics and practical reason are meant 
to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
action.

Not only are vacuous maxims not questions for ethics, but they also represent a 
stronger problem. Asking if you should act while you act undermines your will and thus contradicts
the very idea of willing a maxim. 
Under the Kantian acount of willing, when you will a maxim, you make it your end and commit yourself 
to be its cause. You cannot simultaneously commit yourself to a maxim and ask if you should be committing to it. To 
will the maxim is to decide to will it—so the question, ``should I be 
willing this?" is nonsensical. Either you haven't actually adopted the maxim (and thus haven't yet 
committed yourself to it), or you aren't
actually asking the question (because the decision has already been made). In a vacuous maxim, 
the circumstances already assume that the agent 
has willed the maxim. If someone asks ``should I eat breakfast while eating breakfast?" we not only 
wouldn't be able to answer the question, we wouldn't understand it. Our response would be, ``what 
do you mean? You are already eating breakfast." The agent must either not actually be eating breakfast or 
they must not be asking a real question. This argument is not specific to the Kantian account of willing. 
Under any account of practical action, questioning a commitment as you make the commitment it impossible. 
Either you haven't actually committed or you're not actually asking the question.

@@

"I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
The circumstance ``when dancing" refers 
to rythmically moving your body to music, but ``I should just dance" refers to dancing without anxiety, 
completely focused on the joy of dancing itself. More precisely, this maxim should read ``When 
dancing, I should abandon my anxiety and focus on dancing for the sake of dancing." This maxim when so 
modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
from moving your body rythmically to music. This maxim is actually well-formed, and thus doesn't
pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
on dancing for the sake of dancing itself." The circumstances do not entail the act or the goal because 
they refer to different meanings of the word dancing.

Another interpretation of this example is as follows. Consider the maxim modified to 
read ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
``When dancing and seeing a child drowning" appear to entail the act of dancing, and the maxim thus 
appears vacuous. Once again, this maxim is formulated incorrectly. In this case, the question 
that the agent is actually asking themselves is ``should I continue dancing?" That is the 
maxim that they will adopt or reject. They mean to ask if they should stop dancing and go help the child. 
Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
imply the former but not the latter. A vacuous maxim would have circumstances and act both 
``dancing at moment t," but this maxim has circumstances ``dancing at moment t" and act ``dancing 
at moment t+1." This is a kind of temporal error that has bearings for other debates in ethics as well. 
Specifically, the confusion between circumstances and acts that occur at different times (as in this example) and circumstances 
and acts that occur at the exact same time has bearing on self-doubt, as I will argue next.

@@

Another interpretation of the dancing example is the ``self doubt" intepretation. Under this 
interpretation, the question ``When I am dancing, 
should I be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
right now?" Unlike the drowning example, the agent is not asking about the next moment, but is expressing doubt about the 
moral validity of their behavior at this current moment. I do not want to argue that self-doubt is 
contradictory because it undermines the will—after all, self-doubt plays an important role in moral 
reasoning and often is the mark of a thoughtful agent. I argue instead that questions of self-doubt
do not actually involve vacuous maxims, for these are not the maxims that the agent is doubting. Indeed,
this example demonstrates that the tension between self-doubt and self-respect arises from a 
mistaken characterization of questions of self-doubt as questions about vacuous maxims.
I first explain the tension between self-doubt and self-respect in epistemology, then 
explain the parallel tension in ethics, and finally present a resolution of this tension.

In epistemology, there is a tension between the rational requirement to believe in yourself and the 
value of self-doubt, in moderation. Christensen presents the ``principle of self-respect," which requires 
that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
rationally both believe that the sky is blue and believe that I believe that the sky is green. I cannot 
disapprove of my own credences. Christensen argues that this principle, which he abbreviates to SR, holds because 
a perfectly rational agent can make accurate and confident judgements about what they believe. If this 
is the case, violating SR results in a simple contradiction \cite[8-9]{christensen}.

While most philosophers accept some version of SR\footnote{Van Fraassen, Vickers, Koons \cite[5]{christensen}}, 
Sherrilyn Roush argues that the principle must be modified in order to account for healthy epistemic 
self-doubt. She argues that, while pathological second guessing is roundly criticized, we are generally 
imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Indeed, even Christensen 
acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
requirement to respect our authority as believers and the practical reality that we are often wrong.

This debate between self-respect and self-doubt in epistemology also applies to ethics and practical 
reason. When we decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
validity of our action. If human behavior is purposive, then the very act of committing oneself implies 
that one has sufficient reasons for committing oneself. These reasons may be flawed, but in making the 
commitment, the reasoner has accepted them. It is incoherent to claim that someone commits and questions 
simultaneously, because commitment itself implies a resolution to the question. Either the commitment 
is not real, or the question is not. The principle that 
one cannot will a maxim and simultaneously question if they should will that maxim, is what I will call 
``ethical self-respect" or ESR.

At the same time, self-doubt is an important part of ethical reasoning. Just as believers are often 
mistaken, so are practical reasoners. An agent with perfect confidence, who is always sure that they 
are doing the right thing, is clearly not thinking deeply enough about their obligations. Some degree
of ethical self-doubt is normal and likely desirable. Thus, there is a tension between the rational
requirement of ESR and the intuitive validity of ethical self-doubt (ESD).

To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?" 
What question is she asking here? The immediate answer is that she asking if the maxim, ``When dancing 
at your friend's wedding, dance for the sake of dancing" is a valid maxim to act on. Under this 
simple answer, she is asking if that maxim is prohibited. Notice that the maxim in question is a vacuous
maxim: the circumstance ``when dancing at a friend's wedding" implies the act ``dance." Because it 
is a vacuous maxim, this cannot be the maxim that she is questioning, for adopting this maxim could 
not have changed her behavior at all. Sara is asking a question about her actions and their validity, 
but any conclusions about the validity of a vacuous maxim would not help her, first because the maxim 
has no effect on her action, and second because any such validity would be a foregone conclusion. As 
I argued above, no practical reasoner can coherently ask themselves whether a vacuous maxim is 
valid or not without undermining their decision-making power, which is a contradiction. Thus, under 
the interpretation of self-doubt as a vacuous maxim, the tension between ESR and ethical self-doubt 
appears irresolvable. Those committed to this interpretation must abandon one principle or the other.

@@

%:%462=378%:%
%:%474=380%:%
%:%475=381%:%
%:%476=382%:%
%:%477=383%:%
%:%478=384%:%

@@

%:%528=428%:%
%:%540=431%:%
%:%541=432%:%
%:%542=433%:%
%:%543=434%:%
%:%544=435%:%

@@

>>>>

Once I realized this logical property, I tried to understand its philosophical plausibility. I 
wanted to philosophically test the hypothesis that maxims in which  $(c \longrightarrow a) \vee 
(c \longrightarrow g)$ are not valid inputs to the FUL. I concluded that because vacuous maxims neither 
change an agent's behavior nor generate meaningful obligations, they are not the right kinds of questions 
for practical reasoners to be asking. They cannot be action-guiding and are thus not the domain of ethics.
Moreover, under the Kantian account of the will, the very act of asking if a vacuous maxim is prohibited 
generates a contradiction by undermining the will's authority over itself.

I define a vacuous maxim as one in which the circumstances entail either the act or the goal and argue 
that such maxims can't meaningfully guide action. Consider the example vacuous maxim, ``when eating 
breakfast, I will eat breakfast in order to eat breakfast." This 
maxim isn't clearly obligatory or prohibited, but there is something empty about it. Acting on this
 maxim could never result in any actual action. If an agent adopts this maxim, 
they decide that, in the circumstances ``eating breakfast" they will perform the act ``eating breakfast"
for the purpose ``eating breakfast." In these circumstances, the act has 
already been performed! Treating this maxim a law for yourself or a principle to live by doesn't change 
how you live your life. If you adopt this maxim, when you are eating breakfast, you eat breakfast, 
but this statement is already tautologically true.

Not only does a vacuous maxim fail to prescribe action, any obligations or prohibitions it 
generates have already been fulfilled or violated. If a vacuous 
maxim generates a prohibition, then this prohibition would be impossible to obey. 
It is impossible to not eat breakfast while eating breakfast, because the circumstances assume that the 
act has happened. On the other hand, if a vacuous maxim generates an obligation, then the obligation 
will have already been fulfilled. If you are required to eat breakfast while eating breakfast, then you've 
already fulfilled your obligation because the circumstances assume that the act has happened. Thus, 
a vacuous maxim does not actually guide action because it doesn't generate new obligations or 
prohibitions that could ever be acted on.

Because vacuous maxims can't prescribe or alter action, they are not practically action-guiding and 
thus are not the right kinds of maxims for practical reasoners to evaluate. Moreover, if ethics 
is supposed to guide action, then vacuous maxims cannot be the domain of ethics. Practical reason
is the kind of reason that helps us decide what we should do. 
A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
in order to decide how to act. Practical reason is action-guiding, but a vacuous
 maxim can never be action-guiding because it prescribes no new
actions or obligations. It is not the kind of maxim that a practical reasoner would consider. 
There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
is the wrong kind of question for a practical reasoner to ask. On ordinary person trying 
to navigate the world would never ask that kind of question. If ethics is meant 
to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
action.

Above I argued that vacuous maxims are not the kind of principle that a practical reasoner would ever
ask, and are thus not the right kind of question for ethics. Kantians can make an even stronger claim
about vacuous maxims—because maxims are laws that you give to yourself, asking if you should will 
a maxim as you will it undermines your will's law-giving ability. The circumstances of a vacuous maxim 
already assume that the agent has willed the maxim. Under the Kantian acount of willing, this act 
of willing a maxim is equivalent to giving the maxim to yourself as a law. When you will a maxim, you
adopt a law to make the maxim your end and commit yourself to be its cause. You cannot simultaneously 
commit yourself to a maxim and ask if you should be committing to it. To 
will the maxim is to adopt it as law—so the question, ``should I be 
willing this?" is paradoxical. Either you haven't actually made the maxim your law (and thus haven't yet 
committed yourself to it), or you aren't actually asking the question (because the decision has already been made).
Because a maxim is a law that you give to yourself, you cannot question it absent a sufficient reason 
(such as a change in the circumstances). To question a law arbitrarily is to not regard it as a law at all.
This kind of questioning amounts to questioning the will's authority over itself, but this is 
impossible. The will definitionally has authority over itself, for that is what it is to be a 
will.

@@

Under one reading of this maxim, "I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
The circumstance ``when dancing" refers 
to rythmically moving your body to music, but ``I should just dance" refers to dancing without anxiety, 
completely focused on the joy of dancing itself. More precisely, this maxim should read ``When 
dancing, I should abandon my anxiety and focus on dancing for the sake of dancing." This maxim when so 
modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
from moving your body rythmically to music. This maxim is actually well-formed, and thus doesn't
pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
on dancing for the sake of dancing itself." The circumstances do not entail the act or the goal because 
they refer to different meanings of the word dancing. Any valid reading of this maxim will have the structure above, 
in which the act is actually different from the circumstances. A reasoner cannot accept their will 
as law-giving or commit themselves to an act and simultaneously question the act. Either they must be 
questioning a different act or they must have recieved new information to prompt the questioning, 
modifying the circumstances of the original maxim.

Another related worry has to with maxims that we do in fact think are prohibited. Consider the maxim modified to 
read ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
``When dancing and seeing a child drowning" appear to entail the act of dancing, and the maxim thus 
appears vacuous. Once again, this maxim is formulated incorrectly. In this case, the question 
that the agent is actually asking themselves is ``should I continue dancing?" That is the 
maxim that they will adopt or reject. They mean to ask if they should stop dancing and go help the child. 
Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
imply the former but not the latter. A vacuous maxim would have circumstances and act both 
``dancing at moment t," but this maxim has circumstances ``dancing at moment t" and act ``dancing 
at moment t+1." This is a kind of temporal error that has bearings for other debates in ethics as well. 
Specifically, the confusion between circumstances and acts that occur at different times (as in this example) and circumstances 
and acts that occur at the exact same time has bearing on self-doubt, as I will argue next.

@@

The dancing maxim can also be understood through the lens of self-doubt. Under this 
reading, the question ``When I am dancing, 
should I be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
right now?" Unlike the drowning example, the agent is not asking about the next moment, but is expressing doubt about the 
moral validity of their behavior at this current moment. I do not want to argue that self-doubt always
 undermines the will—after all, self-doubt plays an important role in moral 
reasoning and is often the mark of a thoughtful agent. I argue instead that questions of self-doubt
do not actually involve vacuous maxims, for these are not the maxims that the agent is doubting. Indeed,
this example demonstrates that the tension between self-doubt and self-respect arises from a 
mistaken characterization of questions of self-doubt as questions about vacuous maxims.
I first explain the tension between self-doubt and self-respect in epistemology, then 
explain the parallel tension in ethics, and finally present a resolution of this tension.

In epistemology, there is a tension between the rational requirement to believe in yourself and the 
value of self-doubt, in moderation. Christensen presents the ``principle of self-respect," which requires 
that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
rationally both believe that the sky is blue and believe that I believe that the sky is green. In other words, I cannot 
disapprove of my own credences. Christensen argues that this principle, which he abbreviates to SR, holds because 
a perfectly rational agent can make accurate and confident judgements about what they believe. If this 
is the case, violating SR results in a simple contradiction \cite[8-9]{christensen}.

While most philosophers accept some version of SR\footnote{Van Fraassen, Vickers, Koons \cite[5]{christensen}}, 
Roush argues that the principle must be modified in order to account for healthy epistemic 
self-doubt. She argues that, while pathological second-guessing is roundly criticized, we are generally 
imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Indeed, even Christensen 
acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
requirement to respect our authority as believers and the practical reality that we are often wrong.

This debate between self-respect and self-doubt in epistemology also applies to ethics. When we 
decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
validity of our action. If human behavior is purposive, then the very act of committing oneself implies 
that one has sufficient reasons for committing oneself. These reasons may be flawed, but in making the 
commitment, the reasoner has accepted them. It is contradictory to claim that someone commits and questions 
simultaneously, because commitment itself implies a resolution to the question. Either the commitment 
is not real, or the question is not. I will call the principle that 
one cannot will a maxim and simultaneously question if they should will that maxim
``ethical self-respect" or ESR.

On the other hand, self-doubt is an important part of ethical reasoning. Just as believers are often 
mistaken, so are practical reasoners. An agent with perfect confidence, who is always sure that they 
are doing the right thing, is clearly not thinking deeply enough about their obligations. Some degree
of ethical self-doubt is normal and likely desirable. Thus, there is a tension between the rational
requirement of ESR and the intuitive validity of ethical self-doubt (ESD).

To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?" 
What question is she asking here? The immediate answer is that she asking if the maxim, ``When dancing 
at your friend's wedding, dance for the sake of dancing" is a permissible maxim to act on. Notice that t
he maxim in question is vacuous: the circumstance ``when dancing at a friend's wedding" implies the act 
``dance." Because this is a vacuous maxim, it cannot be the maxim that she is questioning, for adopting 
this maxim could not have changed her behavior at all. Sara is asking a question about her actions and 
their validity. Any conclusions about the validity of a vacuous maxim would not help her, first because 
the maxim has no effect on her action, and second because any such validity would be a foregone conclusion
as she has already adopted the maxim. As 
I argued above, no practical reasoner can coherently ask themselves whether a vacuous maxim is 
valid or not without undermining their will, which is a contradiction. Thus, under 
the interpretation of self-doubt as a vacuous maxim, the tension between ESR and ethical self-doubt 
appears irresolvable. Those committed to this interpretation must abandon one principle or the other.

@@

%:%454=375%:%
%:%455=376%:%
%:%456=377%:%
%:%457=378%:%
%:%458=379%:%
%:%467=383%:%

@@

%:%520=426%:%
%:%521=427%:%
%:%522=428%:%
%:%523=429%:%
%:%524=430%:%
%:%533=433%:%

@@

%:%561=452%:%
%:%562=453%:%
%:%563=454%:%
%:%564=455%:%
%:%565=456%:%
